cardinalR: Generating interesting high-dimensional data structures

### 2025-08-24 paper-cardinalR.Rmd
Updated Figure 12 d

helicalspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "d2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

helicalspiral_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "d3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

>>>>

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.7, 
                                              axis_pos_x = -0.57, 
                                              axis_pos_y = -0.57, 
                                              threshold = 0.05))

helicalspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.75, 0.5), 
  title = "d2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

helicalspiral_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.67), 
  title = "d3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)
